National Longitudinal Evidence for Growth in Subjective Wellbeing from Spiritual Beliefs

### 2020-11-19 Analysis.Rmd
added analysis with centred years for the imputed data set. Inference is the same

#Bifurcated imputation - This is presented in the main text
set.seed(1234)
imputed <- amelia(
  prp, #dataset to impute
  m = 10, # number of imputations
  cs= c("Id"),
  ts= c("Years"),
  noms = c("EthnicCats",
           "Urban",
           "Partner",
           "Male",
           "Employed",
           "Beliefs"),
  idvars=c("Wave","PWI","LIFESAT"), # not imputing outcomes
  polytime = 3) #https://stackoverflow.com/questions/56218702/missing-data-warning-r
#saveRDS(imputed,"imputed")
#imputed<- readRDS("imputed")

# center and scale indiators
imputed.2 <- transform.amelia(imputed,
                              Age.10yrs = (Age/10),
                              Pol.Orient.S =scale(Pol.Orient, center=TRUE,scale=TRUE),
                              Employed = factor(Employed),
                              Ethnicity = as.factor(EthnicCats),
                              Urban = factor(Urban),
                              Deprivation.S = scale(NZdep, scale=TRUE, center=TRUE),
                              Edu.S = scale(Education, scale =TRUE,center=TRUE),
                              Male = as.factor(Male),
                              PWI = as.numeric(PWI),
                              LIFESAT = as.numeric(LIFESAT),
                              Beliefs = as.factor(Beliefs),
                              Id =as.factor(Id))
# center an d scale age
imputed3 <- transform.amelia(imputed.2,
                                     Age.10yrs.C = scale(Age.10yrs,scale =FALSE, center=TRUE))
```

@@

>>>>

#Bifurcated imputation - This is presented in the main text
set.seed(1234)
imputed <- amelia(
  prp, #dataset to impute
  m = 10, # number of imputations
  cs= c("Id"),
  ts= c("Years"),
  noms = c("EthnicCats",
           "Urban",
           "Partner",
           "Male",
           "Employed",
           "Beliefs"),
  idvars=c("Wave","PWI","LIFESAT"), # not imputing outcomes
  polytime = 3) #https://stackoverflow.com/questions/56218702/missing-data-warning-r
#saveRDS(imputed,"imputed")
#imputed<- readRDS("imputed")
```
```{r}

# center and scale indiators
imputed.2 <- transform.amelia(imputed,
                              Age.10yrs = (Age/10),
                              yearsC = scale(Years, center=TRUE,scale=FALSE),
                              Pol.Orient.S =scale(Pol.Orient, center=TRUE,scale=TRUE),
                              Employed = factor(Employed),
                              Ethnicity = as.factor(EthnicCats),
                              Urban = factor(Urban),
                              Deprivation.S = scale(NZdep, scale=TRUE, center=TRUE),
                              Edu.S = scale(Education, scale =TRUE,center=TRUE),
                              Male = as.factor(Male),
                              PWI = as.numeric(PWI),
                              LIFESAT = as.numeric(LIFESAT),
                              Beliefs = as.factor(Beliefs),
                              Id =as.factor(Id))
# center an d scale age
imputed3 <- transform.amelia(imputed.2,
                                     Age.10yrs.C = scale(Age.10yrs,scale =FALSE, center=TRUE))
```

@@

## analysis with centred time (to avoid multicollinearity)

```{r cache = FALSE}
# run models iterating over imputed data
m <- 10
models33 <- NULL
for(i in 1:m) {
  models33[[i]] <- lmer(PWI ~ yearsC * Beliefs + Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data=imputed3$imputations[[i]])
}
```

```{r, cache=FALSE, dependson= models33}
#devtools::install_github("easystats/parameters") Get development version
library(parameters)
mps33 <- lapply(models33, model_parameters)
parameters::pool_parameters(mps33)
mp33<-pool_parameters(mps33)

```{r coef_PWI_imputed_C}
# coeff plot
plot(mp33) + ggtitle("Personal Wellbeing Coefficients (Imputed)") # pick your  own title
```

```{r cache = FALSE, dependson = models3}
## expectation
m<-10
out<-NULL
for(i in 1:m) {
  out[[i]] <- ggpredict(models33[[i]], terms =c("yearsC [minmax]","Beliefs"))
}

m<-10
plots<-NULL
for(i in 1:m) {
  plots[[i]] <- plot(out[[i]], facets = T)# + scale_y_continuous(limits=c(6.35,6.85) )
}
```
```{r, echo=FALSE}
# Inspect all  # No differences
# plots[[1]]
# plots[[2]]
# plots[[3]]
# plots[[4]]
# plots[[5]]
# plots[[6]]
# plots[[7]]
# plots[[8]]
# plots[[9]]
# plots[[10]]
```
```{r predicted_PWI_impute_C}
# to highlight differencs
explectationGraphPWI_C <-plots[[10]] + gghighlight() + ggtitle("Predicted Values of Personal Wellbeing (imputed)")
explectationGraphPWI_C
```
```{r cache =TRUE}
## life sat models
m <- 10
modelsL33 <- NULL

for(i in 1:m) {
  modelsL33[[i]] <- lmer(LIFESAT ~ yearsC * Beliefs + Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban +  (1|Id), data=imputed3$imputations[[i]])
}
```
```{r, cache =FALSE, dependson =  modelsL33}
mpl33 <- lapply(modelsL33, model_parameters)
parameters::pool_parameters(modelsL33)
ml33<-pool_parameters(mpl33)
ml33 # table
p133<-plot(ml3)

p133<- p133 +  labs(title ="Coefficients Life Satisafaction (imputed)")
# get estimates for PWI from above
p233 <- plot(mp133) + labs(title ="Coefficients Personal Wellbeing (imputed)")
```

```{r coefficient_plot_both_imputed_C}
 p233/p133 +  plot_annotation(tag_levels = 'i')
```

```{r, cache =FALSE, dependson = "modelsL3"}
# Expectation plots
m<-10
out2<-NULL
for(i in 1:m) {
  out2[[i]] <- ggpredict(modelsL33[[i]], terms = c("yearsC [minmax]", "Beliefs"),
                         ci.lvl = 0.95,
                         type = "fe",
                         typical = "mean",
                         #   condition = c(Euro =1),
                         back.transform = TRUE,
                         ppd = FALSE,
                         interval = "confidence")
}

library(gghighlight)
```

```{r explectationGraphLS_C}
# Just using one graph
explectationGraphLS_C <-plots2[[10]] + gghighlight() + ggtitle("Predicted Values of Life Satisfaction (imputed)")
```
